Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-19 paper/paper.tex
Update todo
Update Todo
Add way collision statistics table to report
Report: equation centering

\subsection{ESAL, KTH}
The thesis work will be carried out at the Embodied Social Agents Lab (ESAL) at the Department of Computational Science and Technology (CST). The lab has before been working on systems for generating procedural urban environments, and are interested in the possibility of generating more detailed maps than have been done before, using example-based methods to preserve the aesthetic look of a greater metropolitan area. The lab is particularly interested in the generation of footpaths, since most commercial software that import road maps only import arterial and secondary car roads, and do not include pedestrian walkways, cycle paths and such smaller roads.
% TODO: any official description of ESAL that can be used here?

@@

The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion. There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020). The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis. Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files. As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.
%TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

@@

Feature mapping
The building footprint correspondence will be evaluated using a similarity function that assesses the turning funciton and relative area overlap. The similarity function between any building in the OSM data set and any building in the SLU datasets will be defined as a function of their respective footprints ($foot_{OSM}, foot_{SLU}$), as follows:
$S(foot_{OSM}, foot_{SLU}) = S_{T}(foot_{OSM}, foot_{SLU}) + S_{RO}(foot_{OSM}, foot_{SLU})$, where $S_{T}$ measures the difference in turning function and $S_{RO}$ measures the relative overlap between the footprints.

@@

The turning function was first defined by Arkin et al. (1991), as a method for measuring the similarity of two polygons. The Turning function $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l. This project uses the turning function as it is defined by (Fan et al., 2014). For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as: $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions: $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
The value range will be $(0 < S_{T} < 1)$, where $S_{T}(A,B) = 1$ if the polygons are identical.

% TODO: Assign default road widths
% TODO: Implement closest edge distance (project end points on the other edge, get closest perpendicular distance) 
% TODO: Per road, go over nearby features and infer max width, log collisions (max width - min width)

@@

$S_{RO}(foot_{OSM}, foot_{SLU}) = \frac{A_{Overlap}}{min(A_{foot_{OSM}}, A_{foot_{SLU}}))}$

@@

>>>>

\subsection{ESAL, KTH}
The thesis work will be carried out at the Embodied Social Agents Lab (ESAL) at the Department of Computational Science and Technology (CST). The lab has before been working on systems for generating procedural urban environments, and are interested in the possibility of generating more detailed maps than have been done before, using example-based methods to preserve the aesthetic look of a greater metropolitan area. The lab is particularly interested in the generation of footpaths, since most commercial software that import road maps only import arterial and secondary car roads, and do not include pedestrian walkways, cycle paths and such smaller roads.

@@

The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion. There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020). The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis. Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files. As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.

@@

Feature mapping
The building footprint correspondence will be evaluated using a similarity function that assesses the turning funciton and relative area overlap. The similarity function between any building in the OSM data set and any building in the SLU datasets will be defined as a function of their respective footprints ($foot_{OSM}, foot_{SLU}$), as follows:
\begin{center}
    $S(foot_{OSM}, foot_{SLU}) = S_{T}(foot_{OSM}, foot_{SLU}) + S_{RO}(foot_{OSM}, foot_{SLU})$
\end{center}
where $S_{T}$ measures the difference in turning function and $S_{RO}$ measures the relative overlap between the footprints.

@@

The turning function was first defined by Arkin et al. (1991), as a method for measuring the similarity of two polygons. The Turning function $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l. This project uses the turning function as it is defined by (Fan et al., 2014). For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as:
\begin{center}
    $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
\end{center}
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions:
\begin{center}
    $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
\end{center}
The value range will be $(0 < S_{T} < 1)$, where $S_{T}(A,B) = 1$ if the polygons are identical.

% REPORT
% TODO: RELATED WORK, mention current sources (Haklay, Fan)
% TODO: ANALYSIS SECTION, figure out what to write
% TODO: Figure of street, before and after correction, with collision visible in the first half

% TODO: Format formulas
% TODO: Quote Todor's paper for geodata import services and current state of the field

% TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

@@

\begin{center}
    $S_{RO}(foot_{OSM}, foot_{SLU}) = \frac{A_{Overlap}}{min(A_{foot_{OSM}}, A_{foot_{SLU}}))}$
\end{center}

@@

\subsection{Way collision statistics}

\begin{table}[H]
\begin{tabular}{lllll}
                    & Colliding     & Total        & Percent \\
    Features        & 186           & 1951         & 9.53\% \\
    Nodes           & 458           & 264179       & 0.17\% \\
    Edge length     & 14445.66 m    & 5004997.66 m & 0.29\%
\end{tabular}
\end{table}
